---
title: "HW2-chapter5"
author: "Guangjin Zhou"
date: "February 21, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R libraries

```{r warning=FALSE}
library(boot)

library(MASS); 
names(Boston);dim(Boston);str(Boston)
```

# 9. 

We will now consider the Boston housing data set, from the MASS library.

## (a) 

Based on this data set, provide an estimate for the population mean of medv. Call this estimate ^??.

```{r}
mean(Boston$medv)
```

So the estimated ^?? of median Baston area owner-occupied homes  price 22.53 K. 

## (b) 

Provide an estimate of the standard error of ^??. Interpret this result.

Hint: We can compute the standard error of the sample mean by dividing the sample standard deviation by the square root of the number of observations.

```{r}
sd(Boston$medv)/sqrt(nrow(Boston)) 
```

The estimate of standard error of ^?? is 0.4086. This means for the estimate of 22.53K mean house price, about two-thirds (68.3%) of the sample means would be within one standard error:the range between 22.12~22.94K, 95.4% would be within two standard errors:21.72~23.35, the range of  and almost all (99.7%) would be within three standard error: 21.31~23.75.

## (c)

Now estimate the standard error of ^?? using the bootstrap. How does this compare to your answer from (b)?



```{r}
set.seed(471)
meanFunc <- function(x,i){mean(x[i])}

x<-Boston$medv

mean.bt<-boot(data=x,statistic=meanFunc,R=1000);mean.bt; 
```

So by the standard error of medv is 0.4189 by 1000 times bootstrap, it is very close to estimate of standard error of mean 0.4086. 

```{r}
hist(mean.bt$t)
original.mean<-mean.bt$t0; original.mean
bias.mean<-(mean(mean.bt$t)-mean.bt$t0);bias.mean
std.mean<-sd(mean.bt$t);std.mean
```


## (d)

Based on your bootstrap estimate from (c), provide a 95% confidence interval for the mean of medv. Compare it to the results obtained using t.test(Boston$medv).

Hint: You can approximate a 95% confidence interval using the formula [^?? ??? 2SE(^??), ^?? + 2SE(^??)].


```{r}
t.test(Boston$medv)
```

```{r}
upper<-mean(Boston$medv)+2*0.4189001
low<-mean(Boston$medv)-2*0.4189001
ci<-c(mean(Boston$medv),low,upper);ci
```

The 95% confidence interval for medv mean 22.53281 by bootstrap is 21.69501~23.37061.  The t.test 95% confidence interval is 21.72953~23.33608. 

## (e) Based on this data set, provide an estimate, ^??med, for the median value of medv in the population.

```{r}
median(Boston$medv)
```


## (f) 

We now would like to estimate the standard error of ^??med. Unfortunately, there is no simple formula for computing the standard error of the median. Instead, estimate the standard error of the median using the bootstrap. Comment on your findings.

```{r}
set.seed(471)
median.fn<-function(data,index) median(data[index])
x<-Boston$medv
f<-boot(data=x,statistic=median.fn,R=1000);f
```

So the estimate of standard error of ^??med is 0.3813. 

```{r}
hist(f$t)
original.median<-f$t0; original.median
bias.median<-mean(f$t)-f$t0;bias.median
std.median<-sd(f$t);std.median
```


## (g) 

Based on this data set, provide an estimate for the tenth percentile of medv in Boston suburbs. Call this quantity ^??0.1. (You can use the quantile() function.)

```{r}
mu0.1<-quantile(Boston$medv, prob=seq(0,1,0.1)); mu0.1
```

So the 10th percentile of medv in Boston suburbs is 12.75 K.


## (h) 

Use the bootstrap to estimate the standard error of ^??0.1. Comment on your findings.

### 1000 R bootstrap

```{r}
set.seed(471)
my10th<-function(data,index) quantile(data[index],.10)
h<-boot(data=mu0.1,statistic=my10th,R=1000);h
```

### increase R value 

```{r}
set.seed(471)
h2<-boot(data=mu0.1,statistic=my10th,R=100000);h2
```

The standard error of ??0.1 by bootstrap approach is 4.75, this standard error is very large for ??0.1 value 12.75. 

```{r}
hist(h$t, breaks=100);
original.10th<-h$t0; original.10th
bias.10th<-mean(h$t)-h$t0;bias.10th
std.10th<-sd(h$t);std.10th
```

 