---
title: "MLDM_HW1"
author: "Guangjin Zhou"
date: "February 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the library

```{r}
library("ISLR")
```

## (a) Read dataset College

 Use the read.csv() function to read the data into R. Call the loaded data college. Make sure that you have the directory set to the correct location for the data.

```{r}
college<-data.frame(College)
dim(college); str(college)
```

## Remove collge names column

```{r}
fix(college)
```

```{r}
row.names(college)<-NULL;str(college)
fix(college)
```

## (c) Explore the data

### Numerial summary

```{r pressure, echo=FALSE}
summary(college)
```

### II Paired scatterplot matrix to top 10 columns

```{r}
A<-pairs(college[,1:10]);A
```

### IV Plot Out of states student body in private or non-private colleges

```{r}
plot(Outstate~Private, data=college)
```

From the plot, the out-of-state tuitions from private school are higher than non-private schools.

### III Create Elite dummy variable

```{r}
Elite=rep("No",nrow(college )) 
Elite[college$Top10perc >50]=" Yes" 
Elite=as.factor(Elite) 
college=data.frame(college ,Elite);head(college)
```

### Plot out-of-state tuition between elite school and non-elite school

```{r}
plot(Outstate~Elite, data=college)
```

From the plot, the out-of-state tuitions from the elite schools are higher than non-elite school.

### V histograms of quantitative variable

```{r}
par(mfrow=c(2,3))
    
hist(college$Apps)
hist(college$Accept)
hist(college$Enroll)
hist(college$Top10perc)
hist(college$Top25perc)
hist(college$F.Undergrad)
hist(college$P.Undergrad)
hist(college$Outstate)
hist(college$Room.Board)
hist(college$Books)
hist(college$PhD)
hist(college$Grad.Rate)
hist(college$S.F.Ratio)
hist(college$Personal)
hist(college$perc.alumni)
```

### VI Ph.D degree faculites vs elite schools or graduation rate vs elite school

```{r}
plot(PhD~Elite, data=college)
```

It looks that elite schools have much higher rate of Ph.D degree faculties than non-elite schools.


```{r}
plot(Grad.Rate~Elite, data=college)
```

It looks that elite schools have much higher rate of graduation rate than non-elite schools.