---
title: "titantic HW"
author: "Guangjin Zhou"
date: "February 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r message=FALSE, warning=FALSE}
library(titanic); library(gmodels);library(ggplot2);library(vioplot)
```

```{r}
packageDescription("titanic") 
ls("package:titanic") 
```


```{r}
str(titanic_test); dim(titanic_test)
str(titanic_train);dim(titanic_train)
```

```{r}
df<-titanic_train
table(df$Survived)
```

## Cross table of survived and sex

```{r}
CrossTable(df$Survived, df$Sex, chisq = T)
```

Among survived, 68% are female,32% are male. Among died, 15% are female, 85% are male.

## Cross table of survived and passenger seat class

```{r}
CrossTable(df$Survived, df$Pclass,chisq = T)
```

Among survived, 40% have first class,25% have second class and 35% have third class. Among died, 14% have first class,17% have second class and 68% have third class.

## Cross table of survived and siblings

```{r}
CrossTable(df$Survived, df$SibSp,chisq = T)
```

## Cross table of survived and porch

```{r}
CrossTable(df$Survived, df$Parch,chisq = T)
```

```{r}
CrossTable(df$Survived, df$Embarked,chisq = T)
```


## Plot of age by survived

```{r}
boxplot(df$Age~df$Survived,notch=TRUE, col=c("gold","darkgreen"))
```

## Plot of fare by survived

```{r}
boxplot(df$Fare~df$Survived )
```

# Linear Model

## Model1 with majority of variables

```{r}
lm1<-lm(Survived~Pclass+Sex+Age+SibSp+Parch+Fare+Embarked,data=df)      
summary(lm1)
```

## Model2 withoug fare and Age

```{r}
lm2<-lm(Survived~Pclass+Sex+SibSp+Parch+Embarked,data=df)      
summary(lm2)
```

## Model3 with log transformed age

```{r}
lm3<-lm(Survived~Pclass+Sex+SibSp+Parch+Embarked+log(Age),data=df)      
summary(lm3)
```


